Universals of word order result from optimization of grammars for efficient communication

### 2019-01-21 writeup/paper-names.tex
Dependency length

\begin{figure*} % need Efficiency and (maybe) MLE langs on here
\includegraphics[width=0.98\textwidth]{figures/depLength-facet.pdf}
\caption{Average dependency length as a function of sentence length in four languages. Across languages, real and optimized languages have shorter dependencies than random baseline orderings.}\label{fig:deplength}
\end{figure*}

@@

\begin{figure}
    \centering
     \includegraphics[scale=.2]{../results/correlations/figures/posterior-satisfied-universals-efficiency.pdf}
     \includegraphics[scale=.2]{../results/correlations/figures/posterior-satisfied-universals-langmod.pdf}
     \includegraphics[scale=.2]{../results/correlations/figures/posterior-satisfied-universals-parseability.pdf}
     \includegraphics[scale=.2]{../results/correlations/figures/posterior-satisfied-universals-depl.pdf}
	\caption{Posterior of the number of correlations predicted in the direction found in the UD treebanks.}
    \label{fig:posterior-satisfied-count}
\end{figure}

>>>>

\begin{figure*} % need Efficiency and (maybe) MLE langs on here
\includegraphics[width=0.98\textwidth]{../results/dependency-length/figures/depLength-facet.pdf}
\caption{Average dependency length as a function of sentence length in four languages. Across languages, real and optimized languages have shorter dependencies than random baseline orderings.}\label{fig:deplength}
\end{figure*}

@@

\begin{figure}
    \centering
%     \includegraphics[scale=.2]{../results/correlations/figures/posterior-satisfied-universals-efficiency.pdf}
 %    \includegraphics[scale=.2]{../results/correlations/figures/posterior-satisfied-universals-langmod.pdf}
  %   \includegraphics[scale=.2]{../results/correlations/figures/posterior-satisfied-universals-parseability.pdf}
   %  \includegraphics[scale=.2]{../results/correlations/figures/posterior-satisfied-universals-depl.pdf}
     \includegraphics[scale=.45]{../results/correlations/figures/posterior-satisfied-universals-together.pdf}

	\caption{Posterior of the number of correlations predicted in the direction found in the UD treebanks.}
    \label{fig:posterior-satisfied-count}
\end{figure}
